Tools and Ideas for the Procedural Generation of Shadow Sculptures

### 2015-12-16 paper/paper.tex
Changed 'of' to 'or'.

One way this method could be applied to the cylinders is to first divide the cylinders by size. The smaller cylinders can be used with a space-partioning data structure with smaller partitions and the larger ones put in another space partitioning structure of just put in a list and checked at each iteration.

>>>>

One way this method could be applied to the cylinders is to first divide the cylinders by size. The smaller cylinders can be used with a space-partioning data structure with smaller partitions and the larger ones put in another space partitioning structure or just put in a list and checked at each iteration.
